\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}
% \setmain

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{highlight}
}{}{0em}{}[\color{highlight}\titlerule \vspace{-4pt}]

\pdfgentounicode=1
\def\spaceforrole{ }

\newcommand{\sectionspace}{
\vspace{-20pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}

\newcommand{\resumeItem}[1]{
  \item{#1 \vspace{-1pt}} \\
}

\newcommand{\titleItem}[2]{
\vspace{2.5pt}
  \textbf{#1:} &$\space$ \text{#2} \\
}

\newcommand{\experienceTitleAndDate}[2]{
\item
  \textbf{#1} & \hfill  {#2}
}

\newcommand{\experienceCompAndLoc}[2]{
\item
  {#1} & \hfill  \textit{#2}
}

\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
}

\newcommand{\resumeProjectHeading}[4]{
    \item
    \vspace{2pt}
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} | \textnormal{#2} : \textit{#3} & \href{#4}{\color{highlight}Link} \\
    \end{tabular*}\vspace{-20pt}
    \vspace{0pt}
}

\newcommand{\resumeExpHeadingNew}[2]{
\vspace{2px}
    \item
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} & {#2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeExpSubHead}[2]{
    \item
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-20pt}
}

\newcommand{\educationTitleSec}[4]{
    \item
\vspace{2.5pt}
    \begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
        \textbf{#1} -- \textit{\textbf{#2}}, \textit{#3} & {#4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubHeadingListStart}
{
\subheadingtitlevspace
\begin{itemize}[leftmargin=0.00in, label={}]}
\newcommand{\resumeSubHeadingListEnd}
{\end{itemize}}

\newcommand{\resumeItemListStart}{
\begin{itemize}[leftmargin=10pt]}
\newcommand{\resumeItemListEnd}{
\end{itemize}\vspace{-8pt}} % -8pt %

\newcommand{\Certifications}[2]{
    \item
    \textbf{#1}: \textit{#2}
}

\definecolor{highlight}{RGB}{29, 78, 216}

\def\jobLocationMumbai{Mumbai, MH, India}
\def\jobLocationToronto{Toronto, ON, Canada}

\def\jobTitle{Software Engineer}

\hypersetup{
    pdfauthor={Niraj Panchal},
    pdftitle={\jobTitle},
    pdfsubject={\jobTitle 's Resume},
    pdfkeywords={Javascript, Typescript, Python, Swift, Java, Go, C++, HTML, CSS, SASS, 
    Node.js, React, VueJS, Angular, Springboot, Express,
    SQL, NoSQL, MongoDB, Redis, DynamoDB, PostgreSQL,
    Websockets, HTTP, OAuth. REST, API, GraphQL, TCP, RabbitMQ, Kafka
    AWS, Heroku, Jenkins, GCP, Docker, Kubernets
    CI/CD, Git, GitHub, Testing, Jest, Postman, DevOps, DevSecOps,
    Agile, Scrum, Kanban, monitoring system, Grafana, Loki, Prometheus
    problem solving, data structures and algorithms, system design
    },
    pdfproducer={\LaTeX},
    pdfcreator={Visual Studio Code}
}

\begin{document}

\begin{center}
    {\Huge \color{highlight}{\textbf{Niraj Panchal}}} \\
    \vspace{5pt}
    \href{https://linkedin.com/in/nirajp247}{{\textit{LinkedIn}}} $|$
    \href{email@gmail.com}{{\textit{email@gmail.com}}} $|$ 
    \href{tel:+10000000000}{{\textit{+1 (000) 000-0000}}} $|$
    \href{https://github.com/fsd-niraj}{{\textit{Github}}} $|$
    % \href{https://leetcode.com/u/fsd-niraj/}{{\textit{LeetCode}}} $|$
    % \href{https://leetcode.com/u/fsd-niraj/}{{\textit{Medium}}} $|$
    % \href{https://fsd-niraj.github.io/sde-portfolio/}{{\textit{Portfolio}}} $|$
    \textit{\jobLocationToronto}
    \vspace{-8pt}
\end{center}

\section{Skills}
\subheadingtitlevspace
 \begin{itemize}[leftmargin=0.00in, label={}]
    {\item{
 \begin{tabularx}{\linewidth}{@{}l X@{}}
     \titleItem{Tools}{Git, GitHub, GitLab, Postman, Docker, Kubernetes, Jest}
     \titleItem{Technologies}{SQL, NoSQL, Cloud, Grafana, Redis, Kafka, SocketIO}
     \titleItem{Languages}{TypeScript, JavaScript, Swift, Java, Python, Bash}
     \titleItem{Frameworks}{React, Redux, Next.js, Angular, Node.js, Express, Sails}
     % \titleItem{Protocols}{WebSockets, HTTP, RESTful, TCP, UDP, OAuth}
     % \titleItem{Techniques}{Microservices, CI/CD, OOPs, SOLID and ACID Principles, Agile}
\end{tabularx}
    }}
 \end{itemize}
\sectionspace

\section{Experience}
  \resumeSubHeadingListStart
    \resumeExpHeadingNew{Software Developer}{Dec 2020 -- Dec 2022}
        \resumeExpSubHead{Expertrons}{\jobLocationMumbai}
          \resumeItemListStart
            \resumeItem{Integrated Sentry for client-side logs monitoring, helping identify and resolve bugs faster by 2 times.}
            \resumeItem{Led database optimization efforts, achieving a 40\% performance boost for app-wide APIs.}
            \resumeItem{Implemented Redis Caching system which reduced the latency by 75\%.}
            \resumeItem{Created and maintained 4 major test documentation, including test plans, test cases, and test reports of the Web Application.}
            \resumeItem{Participated in architectural discussions and provided technical solutions to improve system scalability and reliability.}
            \resumeItem{Developed a service that transfers client's data into the sales and business team’s portal on time.}
            \resumeItem{Recognized as a Q1 Star Performer.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
% \sectionspace


\section{Projects}
  \resumeSubHeadingListStart
  
    \resumeProjectHeading{POS System}{Web App}{React, Redux, Tailwind, Nodejs, MongoDB, Redis, JWT, Vite}{https://github.com/fsd-niraj/cashMate}
          \resumeItemListStart
                \resumeItem{Designed and implemented a POS system, optimized for small-scale, offline operations to ensure fast and reliable transaction processing.}
                \resumeItem{Integrated a responsive user interface with Redux for state management, improving cashier efficiency and reducing transaction times in a local environment.}
           \resumeItemListEnd

    \resumeProjectHeading{Server Observability System}{Web, Desktop}{Grafana, Prometheus, Loki, Nodejs, Express, Docker}{https://github.com/fsd-niraj/server-Observability-System}
        \resumeItemListStart
            \resumeItem{Collected metrics like methods, route, status code, time of an API and a specific route with the help of Prometheus.}
            \resumeItem{Efficiently visualized the collected data in Grafana and collected logs using Grafana Loki.}
       \resumeItemListEnd 
       
    \resumeProjectHeading{NFT Visualization}{Cross Platform (Android, iOS)}{React Native, Styled Components, Expo}{https://github.com/fsd-niraj/nft_app}
          \resumeItemListStart
                \resumeItem{Developed a cross-platform NFT app using React Native, helping users get a detailed view of their portfolio and leaderboard.}
           \resumeItemListEnd
           
    \resumeProjectHeading{Centralised Crypto Exchange}{Web App}{Next.js, Prisma, Postgresql, solana-Web3}{https://github.com/fsd-niraj/SecureXchange}
          \resumeItemListStart
                \resumeItem{Coded a centralized crypto exchange platform, allowing a user to swap and stake their crypto in a very secure way.}
           \resumeItemListEnd

    \resumeProjectHeading{DNS Server}{Software}{Typescript, Git, CLI}{https://github.com/fsd-niraj/dns-server}
        \resumeItemListStart
            \resumeItem{An MVP of a DNS Server capable of handling questions and providing answers while maintaining request records.}
       \resumeItemListEnd
       
    \resumeProjectHeading{Admin Dashboard}{Web App}{React, Redux, TypeScript, Material UI}{Link}
        \resumeItemListStart
            \resumeItem{Designed and developed a comprehensive frontend dashboard using React and Redux for state management.}
            \resumeItem{Optimized for a mobile-first experience, improving accessibility and user satisfaction.}
       \resumeItemListEnd
       
    \resumeProjectHeading{Mars Image viewer}{iOS}{ Swift, X-Code, MVC}{https://github.com/fsd-niraj/mars-image-viewer}
        \resumeItemListStart
            \resumeItem{Replaced JSON data with Google Maps API and made more than 1000 locations available to search.}
            \resumeItem{Ranked first in the class with additional functionality over other students.}
       \resumeItemListEnd
        
  \resumeSubHeadingListEnd
% \sectionspace

\section{Certifications}
\subheadingtitlevspace
 \begin{itemize}[leftmargin=0.00in, label={}]
    {\item{
 \begin{tabularx}{\linewidth}{@{}l X@{}}
  \titleItem{Hacker Rank}{JavaScript, Nodejs, React}
  \titleItem{Microsoft}{Cyber \& Mobile Security}
  \titleItem{Uni. of Michigan}{Python (Analytics \& AI)}
\end{tabularx}
    }}
 \end{itemize}
\sectionspace

\section{Education}
  \resumeSubHeadingListStart
  \educationTitleSec{Post graduate in Web \& Cloud Design and Development}{Humber College}{\jobLocationToronto}{April 2024}
  \educationTitleSec{Post graduate in Enterprise Software Development}{Humber College}{\jobLocationToronto}{Aug 2023}
  \educationTitleSec{Bachelor of Computer Application}{YCMOU}{\jobLocationMumbai}{June 2020}
  \resumeSubHeadingListEnd
% \sectionspace

\section{Publications}
   \begin{itemize}[leftmargin=0.00in, label={}]
    {\item{
 \begin{tabularx}{\linewidth}{@{}l X@{}}
  \titleItem{Medium Blogs}{\href{https://medium.com/@fsd-niraj}{\color{highlight}https://medium.com/@fsd-niraj}}
\end{tabularx}
    }}
 \end{itemize}
% \sectionspace

\end{document}